A voice within the tower called loudly:
—Are you up there, Mulligan?
—I’m coming, Buck Mulligan answered.
He turned towards Stephen and said:
—Look at the sea. What does it care about offences?
Chuck Loyola, Kinch, and come on down. The Sassenach
wants his morning rashers.
His head halted again for a moment at the top of the
staircase, level with the roof:
—Don’t mope over it all day, he said. I’m
inconsequent. Give up the moody brooding.
His head vanished but the drone of his descending
voice boomed out of the stairhead:
\textit{And no more turn aside and brood}
\textit{Upon love’s bitter mystery}
\textit{For Fergus rules the brazen cars.}
Woodshadows floated silently by through the morning
peace from the stairhead seaward where he gazed. Inshore
and farther out the mirror of water whitened, spurned by
lightshod hurrying feet. White breast of the dim sea. The
twining stresses, two by two. A hand plucking the
harpstrings, merging their twining chords. Wavewhite
wedded words shimmering on the dim tide.
A cloud began to cover the sun slowly, wholly,
shadowing the bay in deeper green. It lay beneath him, a
bowl of bitter waters. Fergus’ song: I sang it alone in the
house, holding down the long dark chords. Her door was
open: she wanted to hear my music. Silent with awe and
pity I went to her bedside. She was crying in her wretched
bed. For those words, Stephen: love’s bitter mystery.
Where now?
Her secrets: old featherfans, tasselled dancecards,
powdered with musk, a gaud of amber beads in her locked
drawer. A birdcage hung in the sunny window of her
house when she was a girl. She heard old Royce sing in
the pantomime of Turko the Terrible and laughed with
others when he sang:
\textit{I am the boy}
\textit{That can enjoy}
\textit{Invisibility.}
Phantasmal mirth, folded away: muskperfumed.
\textit{And no more turn aside and brood.}
